Manuscript drafts

### 2020-03-11 manuscript/drafts/manuscript.Rmd
- add classification problem - add datsets info - add classifiers - update meeting notes

@@

[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas Naïve Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision. The AUC results are mixed, although boosting has a slight edge overall. These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, Naïve Bayes for sensitivity, and boosting for balance between the two, for example)."

@@

\newpage
# Methods
Goal: evaluate performance of different models of the ASReview tool. 
The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
What would happen if the citation screening would have been performed using asreview?

@@

#### ace 
A dataset from a collection of systematic reviews on drug efficacy from the medical sciences [@Cohen2006]. 
This dataset is on a systematic review

efficacy of Angiotensin-converting enzyme (ACE) inhibitors.
The ace dataset comes from a study on reducing workload in systematic reviews  [@Cohen2006].
The ace dataset is on the efficacy of

drug class 
The ACEInhibitors dataset from the study by [@Cohen2006].
The study includes several data sets from the medical sciences, one of them is on ACE inhibitors.

a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy.

WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
The data

#### software 
A review on fault prediction in software engineering by [@Hall2012]. 
The dataset is reviewed from [@Yu2018a] who collected datasets on literature reviews from the software engineering field.

#### nudging
review [@Nagtegaal2019]
The data [@Nagtegaal2019a]

Difference in 18 inclusions = systematic reviews. to exclude/include?

#### ptsd
A review [@vandeSchoot2018] on longitudinal studies on posttraumatic stress symptoms assessed after exposure to trauma. 
The corresponding dataset [@Winter2020].

#### Wilson
The review [@Appenzeller-Herzog2019]
The dataset [@Appenzeller-Herzog2020]

Statistics on the SRs can be found in `r table_nums("datasets", display = "cite")`. 
All datasets accompanying the systematic reviews are openly published. 
The datasets contain information on all citations obtained in the search strategy and which citations were included in the systematic review.

For every SR, the raw datafiles were preprocessed into a test dataset.

These test datasets contain authors, title, abstract and annotation of whether the entry was included in the final review or not (0/1).

Entries with missing abstracts were removed. 
Duplicate entries were removed. 
Preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]

@@

#### Classifiers
The classifier predicts the class of all papers. 
To predict whether a paper should be an exclusion or an inclusion, different classifiers

- Naive Bayes (B)
- Random Forests (R)
- Support Vecor Machine (S)
- Logistic Regression (L)
- Dense Neural Network (N)

@@

A classical example is a 'bag of words' representation. 
For each each text, the number of occurrences of each word is stored. 
This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].

We use the following feature extraction methods
- TF-IDF

@@

@@

#### Assumptions

 - decisions of the original SR are **ground truth** (benchmark) (oracle)
 - binary classifications: relevant/irrelevant

@@

#### TF-IDF
The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and".

Term-frequency Inverse Document Frequency [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire corpus.

@@

>>>>

Binary classification problem. 
predict whether a paper in the pool is an inclusion or exclusion, 
based on labeled instances from $\mathcal{L}$ and use training data to understand how input variables are related to class.

We're building active learning model who takes X as an input an predicts class using labels from training set. 
Model improves by deciding asking more information from the reviewer (oracle), 
accounting for imbalance.

#### Assumptions 
1) decisions of the original SR are **ground truth** (benchmark) (oracle)

Datasets from the medical and social sciences, software engineering and public administration. 
Medical sciences SRs are viewed as more 'strict'/'structured' and social sciences more messy.

@@

[@Kilicoglu2009] - SVM, naive bayes, boosting and combinations. future work should optimize parameters.
  "Regarding the base classifiers used in identifying method- ologically rigorous studies, boosting consistently strikes the best balance between precision and recall, whereas naive Bayes in general performs well on recall (demonstrating a tradeoff between recall and precision), as does polynomial SVM on precision. The AUC results are mixed, although boosting has a slight edge overall. These results demonstrate that different classifiers can be used to satisfy different information needs (SVM for specificity, naive Bayes for sensitivity, and boosting for balance between the two, for example)."

@@

This study was approved by the Ethics Committee of the Faculty of Social and Behavioural Sciences of Utrecht University, filed as an amendement under study 20-104, ASReview - Smart software for Systematic Reviews.

All simulations were run using through caartesius EINF-156

\newpage
# Methods
Goal: evaluate performance of different models of the ASReview tool. 
The screening process is simulated using ASReview, seeing if the original inclusions replicate. 
What would happen if the citation screening would have been performed using asreview? 
All datasets accompanying the systematic reviews are openly published.

@@

#### ace 
Cohen et al. collected systematic review datasets from the medical sciences [@Cohen2006]. 
All systematic reviews in this database are on drug efficacy. 
The ace dataset used in the current study comes from a systematic review on the efficacy of Angiotensin-converting enzyme (ACE) inhibitors.

a machine learning-based citation classification tool to reduce workload in systematic reviews of drug class efficacy. 
Using a perceptron classifier, WSS@95% = 56.61 in [@Cohen2006]. (5x2 crossvalidation). Can we beat this? 
The data

#### software 
The dataset is retrieved from [@Yu2018a], who collected datasets on literature reviews from the software engineering field. 
This dataset is on fault prediction in software engineering by [@Hall2012].

#### nudging
A review from the behavioural public administration area. 
The SR includes studies on nudging healthcare professionals [@Nagtegaal2019]. 
The data was stored on the Harvard Dataverse [@Nagtegaal2019a].

#### ptsd
A literature review from field of psychology. The SR is on studies applying latent trajectory analyses on posttraumatic stress after exposure to trauma [@vandeSchoot2017]. 
The corresponding dataset can be found on the Open Science Framework [...].

#### Wilson
A dataset from the medical sciences [@Appenzeller-Herzog2020]. 
TA review on effectiveness treatments of Wilson disease [@Appenzeller-Herzog2019].

All datasets started with an initial pool of thousands of papers. 
A fraction of these papers where deemed relevant for the SR, with inclusion rates varying from .. to .. (`r table_nums("datasets", display = "cite")`).

The raw datafiles published with the SRs were preprocessed into a test dataset.
The test datasets contain title information on all citations obtained in the search strategy. 
The instances in the data consist of a title, an abstract and were labeled to indicate which citations were included in the systematic review. 
Instances with missing abstracts were removed. 
Duplicate instances were removed. 
Preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]

@@

#### Classifiers
The classifier predicts the class of all papers, given the training dataset/labeled data set $\mathcal{L}$.

Given the labels and some features from all abstracts in the pool, the classifier 
To predict whether a paper should be an exclusion or an inclusion, different classifiers

Naive Bayes (B) - predicts the class of an instance given input features $\mathbf{X}$. Naive Bayes assumes all features are independent given the class value. This is obviously not the case but still the algorithm performs impressively [@Zhang2004]. Especially at ... tasks.

Random Forests (R) is where a large number of decision trees are fit on bootstrapped samples of the original data.
All trees cast a vote on the class, which are aggregated into a class prediciton for each input $\mathbf{X}$ [@Breiman2001].

Support Vecor Machine (S) - finds a multidimensional hyperplane to separate classes.
[@Tong2001]

Logistic Regression (L) -

Dense Neural Network (N) -

@@

A classical example is a 'bag of words' representation. 
For each each text, the number of occurrences of each word is stored. 
This leads to n features, where n is the number of distinct words in the texts [@scikit-learn].
The bag-of-words method is simplistic and will highly value often occuring but otherwise meaningless words such as "and". 
Term-frequency Inverse Document Frequency (TF-IDF) [@Ramos2003] circumvents this problem by adjusting a term frequency in a text with the inverse docuement frequency, the frequency of a given word in the entire corpus.

(T) (D)

@@

When no balancing is applied, the training data set = labeled data set $\mathcal{L}$

@@

@@

#### TF-IDF

@@

 Arguments
        ---------
        gamma: str
            Gamma parameter of the SVM model.
        class_weight:
            class_weight of the inclusions.
        C:
            C parameter of the SVM model.
        kernel:
            SVM kernel type.
        random_state:
            State of the RNG.
